### 2017-04-06 paperMVVB/sections/content.tex
implemented cubehelix color scheme for 1 plot

In comparison with the data the fit models roughly match with the general trends (Fig.~\ref{fig:OMNI_yearly_BVNTSSN_fit_b_plot}).\\
\begin{figure*}
	\includegraphics[width=18cm]{figures/OMNI_yearly_BVNTSSN_fit_b_plot.pdf}
	\caption{Solar wind parameter frequencies, lognormal fit models and the corresponding yearly SSN (grey) over the OMNI time period 1963--2016. The for the model shifted SSN is indicated by a black line.}
	\label{fig:OMNI_yearly_BVNTSSN_fit_b_plot}
\end{figure*}

>>>>

In comparison with the data the fit models roughly match with the general trends (Fig.~\ref{fig:OMNI_yearly_BVNTSSN_fit_c_plot}).\\
\begin{figure*}
	\includegraphics[width=18cm]{figures/OMNI_yearly_BVNTSSN_fit_c_plot.pdf}
	\caption{Solar wind parameter frequencies, lognormal fit models, their median values (white) and the corresponding yearly SSN (grey) over the OMNI time period 1963--2016. The for the model shifted SSN is indicated by a black line.}
	\label{fig:OMNI_yearly_BVNTSSN_fit_c_plot}
\end{figure*}
